Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex

The paper is structured as follows. In \cref{sec:example}, we will walk through a function
call in a simple example machine and discuss how each of our properties applies to it,
informally. In the process we discuss some motivation for the properties, from a security
perspective. We consider a simple attacker, and discuss the harm that it can do to
its caller. This perspective is essential to understanding how lazy enforcement can
be safe: even if an attacker can overwrite some memory, if it cannot accomplish
its bigger-picture goals, the system is safe.

Then in \cref{sec:machine} we will introduce the machine model that we test, and give
its {\em security semantics}, described in brief below. We formalize the definitions of
stack safety that derive from the security semantics in \cref{sec:props}.
\Cref{sec:testing} describes the testing framework, and
\cref{sec:relwork,sec:future} discuss related and future work.
The remainder of this section introduces ideas that will be important throughout.

@@

>>>>

\apt{Not a good place for this.}
The paper is structured as follows. In \cref{sec:example}, we will walk through a function
call in a simple example machine and discuss how each of our properties applies to it,
informally. In the process we discuss some motivation for the properties, from a security
perspective. We consider a simple attacker, and discuss the harm that it can do to
its caller. This perspective is essential to understanding how lazy enforcement can
be safe: even if an attacker can overwrite some memory, if it cannot accomplish
subvert the observable behavior of the caller, the system is safe.

In \cref{sec:machine} we formalize the machine model, 
its {\em security semantics}, and the stack safety properties built on these. 
\Cref{sec:testing} describes the testing framework, and
\cref{sec:relwork,sec:future} discuss related and future work.
The remainder of this section introduces ideas that will be important throughout.

@@

\apt{Something about how the machine can incorporate enforcement, with examples
(tags, capabilities, SW only). }
